LCS Tool — An Algorithmic Introduction to Lagrangian Coherent Structures

### 2014-02-17 main.tex
Small changes to colortracer paragraph

A further point important to note is the coexistence of hyperbolic and elliptic LCS. The examples we present show hyperbolic LCSs inside elliptic LCSs. This may seem contradictory when accustomed to LCSs not crossing, however, numerical experimentation with LCS calculations overlaid with color tracer advection reveals that hyperbolic LCS can cross elliptic barriers and have an impact on the tracer pattern inside elliptic regions. At crossing points a line segment of an elliptic LCS, oriented along $\boldsymbol \eta_\lambda^{\pm}$, does not stretch, while a segment of a strainline, oriented along $\boldsymbol \xi_1$, repels fluid normally at a maximal rate and shrinks at a maximal rate. Figure~\ref{fig:ocean_dataset_colortracer} illustrates the effect of strainlines on tracer particles inside elliptic regions. Color-coded final positions show large gradients along strainlines, directly showing that particles are strongly repelled by the LCS and end in different positions.

>>>>

A further point important to note is the existence of hyperbolic LCS inside elliptic LCS.
This may seem contradictory when accustomed to LCSs not crossing, however, numerical experimentation with LCS calculations overlaid with color tracer advection reveals that hyperbolic LCS can cross elliptic barriers and have an impact on the tracer pattern inside elliptic regions. At crossing points a line segment of an elliptic LCS, oriented along $\boldsymbol \eta_\lambda^{\pm}$, does not stretch, while a segment of a strainline, oriented along $\boldsymbol \xi_1$, repels fluid normally at a maximal rate and shrinks at a maximal rate. Figure~\ref{fig:ocean_dataset_colortracer} illustrates the effect of strainlines on tracer particles inside elliptic regions. Color-coded final positions show large gradients along strainlines, directly showing that particles are strongly repelled by the LCS and therefore end in different positions.
